Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-11-14 docs/00-manuscripts/mdpi/manuscript.tex
update selected features part WRT to changes of results

% Selected percentage of features across plots
FIXME:
The number of features selected based on model tuning strongly varied across learners and plots.
While for RF, the least features were selected when Luiando or Oiartzun was the test set ($n = 1$), more than 90\% of all features were used for test sets~Laukiz1 and Laukiz2 (\autoref{tab:tune-perc-sel-features}).
RF and SVM used very few features only when Laukiz1 was the test set (three and one, respectively) whereas this was the plot for which XGBoost used almost all features ($n = 1226$).
Overall, SVM used the least features across all plots and among all learners, the highest\ single fraction being 24\% for test set~Laukiz2.
In general, all learners behaved rather differently on the various plots, and therefore no overall pattern could be identified.

@@

FIXME:
The most important features for datasets HR and VI showed an average decrease in RMSE of 1.06 p.p. (HR, B69) and 1.93 p.p. (VI, Vogelmann2) (\autoref{fig:fi-permut-vi-hr}).
For the HR dataset, most (i.e., six out of ten) relevant features clustered around the infrared region (920~nm - 1000~nm), while for VI, eight out of ten concentrate within the wavelength range of 700~nm - 750~nm (the so\-/called \enquote{red edge}).
For HR, four features in the infrared region (920~nm - 1000~nm) were identified by the model to be most important, being associated with a mean decrease in RMSE of around 1 p.p.
Overall, apart from the top five features, the vast majority of features showed only a small importance with average decreases in RMSE below 0.5 p.p.

@@

FIXME:
Arbitrary seeming values of selected feature percentages like 99.97268\% in \autoref{tab:tune-perc-sel-features} emerge from the specific setting which got elected as the best setting during the tuning step.
The specific value to benchmark during tuning is defined by the internal surrogate learner of the MBO tuning method in this study and can be any numeric value between 0 and 1 (interpreted as a\ percentage of available features).

>>>>

% Selected percentage of features across plots
The number of features selected during model optimization strongly varied across learners and plots.
RF selected the least features of all three learners, and with the expection of Oiartzun, only one or two variables got selected.
SVM used 210 features or more in all instances and varied between 16\% (Laukiz1) - 81\% (Oiartzun) (\autoref{tab:tune-perc-sel-features}).
XGBoost also favored using several hundred features with the exeption of Laukiz2 for which only 14 (0.96\%) were selected.

@@

The most important features for datasets HR and VI showed an average decrease in RMSE of 1.06 p.p. (HR, B65) and 1.93 p.p. (VI, Vogelmann2) (\autoref{fig:fi-permut-vi-hr}).
For the HR dataset, most (i.e., six out of ten) relevant features clustered around the infrared region (920~nm - 1000~nm), while for VI, eight out of ten concentrate within the wavelength range of 700~nm - 750~nm (the so\-/called \enquote{red edge}).
For HR, four features in the infrared region (920~nm - 1000~nm) were identified by the model to be most important, being associated with a mean decrease in RMSE of around 1 p.p.
Overall, apart from the top five features, the vast majority of features showed only a small importance with average decreases in RMSE below 0.5 p.p.

@@

Arbitrary seeming values of selected feature percentages in \autoref{tab:tune-perc-sel-features} emerge from the specific hyperparameter setting which got elected as the best one during the tuning step.
The specific performance value to benchmark against during tuning is defined by the internal surrogate learner of the MBO tuning method and can be any numeric value between 0 and 1 (interpreted as a\ percentage of available features) for the hyperparameter that controls the number of features.
